\documentclass[line, margin]{res}
\usepackage{enumitem}
\usepackage{url}


\begin{document}
\name{Michael Harpe}
\address{1604 Swinton Ln\\ Henrico, VA 23238\\ (804) 543-0554\\ michael@harpelife.com} 
 
\begin{resume}

\section{EDUCATION} 
 \textit {James Madison University}, Harrisonburg, VA \\
 Bachelor of Science in Computer Science \hfill May 2012\\
 Minor in Telecommunications \\

\section{KEY COURSES}

\begin{itemize}[itemsep=2pt,leftmargin=10pt]
\item Local Area Networks 
\item Internetworking 
\item Information Security 
\item Cyber Defense 
\item Multimedia Design
\end{itemize}


\section{SKILLS}
\begin{itemize}[leftmargin=10pt]
\item C\#, SQL, JAVA, BASH, PHP, JavaScript, Python, Powershell, VBScript
\item Systems Administration of Windows and Linux Systems
\item Installing and running Exchange Server, IIS, Active Directory, DNS, Apache, Nginx, DHCP
\item Ability to configure CISCO IOS devices
\item Ability to use network analysis tools: NESSUS, Nmap, etc.
\item Ability to set up a VPN server
\item Basic understanding of VOIP protocols
\item Knowledge of installing and running Asterisk PBX
\item Ability to set up and run NFS servers
\item Installing and running VMWare, ESXI, VSphere
\end{itemize}

\section{EXPERIENCE} 
\textbf{UPS - Freight} \textit{Applications Developer} \hfill February 2016 - Present \\
As an application developer I was responsible for developing and supporting internal user applications. I developed software in C\# and supported applications that were already built. I was in charge of several projects from implementing them to overseeing the deployment of them.\\ [10pt]
\textbf{Southeastern Underwriters} \textit{IT Tech} \hfill May 2012 - February 2016 \\
As an IT Tech my responsibilities include performing help desk tasks by troubleshooting and solving employee computer software and hardware problems. I administer the windows servers on the company's network. I design and implement in house insurance software systems written in C\# using the agile development method, as well as building the corresponding Visual Foxpro databases to process data and display it to employees in a user friendly manner. I oversee these projects from start to finish, from collecting requirements to building the whole system. I have worked on large scale projects that were in development for 6 months as well as smaller projects that make day to day processes more efficient. My job also requires direct communication with our company's clients to resolve website related issues.\\ [10pt]
\textbf{JMU CampusNET} \textit{Computer Support Tech} \hfill Aug 2011 - May 2012 \\
As a student employee I was tasked with troubleshooting and diagnosing hardware and software problems on student's computers, including networking issues, virus removal, and recovering files after a hard drive crashes.\\ [10pt]
\newpage
\textbf{International Mission Board} \textit{Global Technology Services Intern} \hfill Summer 2011 \\
As a summer intern I assisted in a full system development life cycle using the Agile development method. I gathered information from users to determine software requirements. I designed and developed asp.net web pages in C\# allowing users to input data. Using SQL Server Management Studio I wrote queries and stored procedures, to retrieve and store data from the company database. I also tested the web pages and created a test group from the user base.\\ [10pt]
\textbf{International Mission Board} \textit{Desktop Services Intern} \hfill Summer 2010 \\
As a summer intern I diagnosed and repaired software and hardware issues on employee computers. I created hard drive images and then used them to image multiple computers at once. I installed computer encryption software on employees computers before they relocated overseas. I oversaw disposing of old computers that were no longer functional by wiping hard drives and recycling the remaining parts. \\ [10pt]

\section{HONORS}
\begin{tabular}{@{}l l}
August 28, 2007 & \textbf{\textit{Eagle Scout Award}} \\ [5pt]
March 2011 & \textbf{\textit{Second Place in Mid-Atlantic Regional CCDC}} \\ [5pt]
March 2012 & \textbf{\textit{Third Place in Mid-Atlantic Regional CCDC}} \\ [5pt]
May 2012 & \textbf{\textit{Information Systems Security Professionals Certificate}} \\ [5pt]
April 2012 & \textbf{\textit{Inducted into Upsilon Pi Epsilon Honor Society}} \\ [5pt]
April 2012 & \textbf{\textit{JMU CS Leonard Lapadula Award}} \\
\end{tabular}

\section{PERSONAL PROJECTS}
\textbf{Care Ministries Record System} \textit{2015} \\
I built a website for the Care Ministries food pantry record system. The site was developed in PHP using Laravel as a MVC framework. The site allows users to keep track of client records as well as create reports based on demographics of the clients.

\textbf{Binarytees} \textit{2014} - \textit{Depricated} \\
Binarytees was a website I built with a friend that sold custom made geeky shirts. I developed it in PHP, JQuery, and MySQL. The site allowed users to purchase shirts from us, where the orders would then be sent to a print on demand service using their API. 

\textbf{Harpelife Website} \textit{On Going} \hfill \url{http://harpelife.com} \\
I created a personal website that displays photos and manages them within albums. The website was written in C# using ASP.NET Core and MVC framework.

\textbf{Home Network} \textit{On Going} \\
I created an extensive home network that includes multiple virtual servers running on Citrix XenServer. I setup Windows Servers running Active Directory, DNS, and DHCP. I also created a network file share system, and a PBX phone system to use as our home phone.

\end{resume}
\end{document}
